\section{Introduction}

Two-dimensional (2D) crystalline materials exhibit an important sensitivity to structural imperfections. In 2D systems, topological defects such as dislocations and grain boundaries play a central role in determining both structural and functional properties \cite{Mermin1968}, as their elastic fields extend over large distances. Graphene is a particularly relevant physical realization of this paradigm. Large-area graphene samples are commonly polycrystalline, consisting of multiple crystallites with different orientations and separated by grain boundaries. These grain boundaries are not only geometric imperfections but constitute extended topological defects composed of periodic arrays of dislocations. They have been extensively investigated, revealing a strong dependence on the relative misorientation between neighboring grains \cite{Yazyev2010}.

From a theoretical perspective, grain boundaries in graphene can be understood as arrays of dislocations whose spacing is controlled by the misorientation angle. In the low-angle regime, this description naturally leads to the Read--Shockley form of the grain-boundary energy \cite{Read1950}. Grain boundaries also raise important questions concerning the statistical mechanics of orientational degrees of freedom in polycrystalline graphene. In particular, the possibility of nontrivial orientational phases. In two dimensions, such phases are known to be strongly constrained by topology, as conventional long-range order is prohibited in the presence of continuous symmetries \cite{Mermin1966}. Instead, orientational order may persist only in a quasi-long-range form.

Polycrystalline graphene is closely related to the class of two-dimensional systems described by the Kosterlitz--Thouless--Halperin--Nelson--Young (KTHNY) theory of melting \cite{Kosterlitz1973,Nelson1978,Nelson1979,Young1979}. While KTHNY theory was originally developed for atomic and molecular crystals, its underlying principles are more general and can, in principle, apply to coarse-grained orientational degrees of freedom.

In this work, we explore these ideas through a coarse-grained model of polycrystalline graphene. Each crystallite is represented by a single orientational variable, and the energetic cost of misorientation between neighboring grains is encoded using a Read--Shockley interaction. An additional substrate coupling term favors global alignment \cite{Rogge2015}. Using Monte Carlo simulations, we investigate the thermal behavior of this model and characterize the resulting orientational phases through bond-orientational correlation functions and susceptibilities. We first reproduce well-established results for the two-dimensional XY model \cite{Kosterlitz1973} and then analyze the polycrystalline model, demonstrating the emergence of a phase transition. The present study thus verify that the KTHNY theory can be applied to this coarse-grained model of polycrystalline graphene.
